\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation of timber volume resources on forest district levels \\ \vspace{2ex} \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}

### 2017-12-18 Draft_Form/tex/Materials_and_Methods.tex
Initial commit 18_12_2017
Initital commit

@@

\section{Terrestrial sampling design of the German NFI}
\label{sec:germanNFI}

@@

% ++++++++++++ %
\section{Double sampling in the infinite population approach}
\label{sec:inf_pop}

@@

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\section{Estimators}
\label{sec:estimators}

% ++++++++++++ %
\subsection{Design-based SRS estimator for cluster sampling}
\label{sec:srs_estimator}

The simple random sampling (SRS) estimator for cluster sampling constitutes the \textit{status quo} that is currently applied under the existing one-phase sampling design of the German NFI in order to obtain a point and variance estimate for the mean timber volume of a given estimation unit. In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator that is applied in the BWI3 algorithms \citep{bwi3_ausw} in the form given in \citet{mandallaz2008, mandallaz2016}.\par 
In order to calculate the local density $Y_{c}(x)$ at the cluster level, a cluster is defined as consisting of $M$ sample locations (in the BWI3, we have $M=4$ ) where $M-1$ sample locations $x_2, ..., x_M$ are created close to the cluster origin $x_1$ by adding a fixed set of spatial vectors $e_2, ..., e_M$ to $x_1$. The actual number of plots per cluster, $M(x)$, is a random variable due to the uniform distribution of $x_l$ ($l=1, ..., M$) in the forest $F$ and forest/non-forest decision for each sample location $x_l$:

@@

% +++++++++++++++++++++++++++++ %
\subsection{Design-based small area regression estimators for cluster sampling}
\label{sec:SAestimators}

@@

% ----------------------------- %
% PSMALL estimator:
\subsubsection{Pseudo Small Area Estimator (\psmall{})}
% \textbf{Pseudo Small Area Estimator (\psmall{})}\\

@@

The estimated design-based variance of $ \hat{Y}_{c,G,PSMALL}$ is given by Eq. \ref{eq:psmall_var}. Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean in $G$ using a non-exhaustive sample $s_{1,G}$. The third term is the variance of the model residuals and thus accounts for the inaccuracies of the model predictions. Note that the first term can also be rewritten using g-weights \cite[pg.14]{mandallaz2016} which ensure calibration properties of the auxiliary variables on the terrestrial sample.\\

@@

% ----------------------------- %
% PSYNTH estimator:
\subsubsection{Pseudo Synthetic Estimator (\psynth{})}
% \textbf{Pseudo Synthetic Estimator (\psynth{})}\\

@@

% ----------------------------- %
% EXTPSYNTH estimator:
\subsubsection{Extended Pseudo Synthetic Estimator (\extpsynth{})}
% \textbf{Extended Pseudo Synthetic Estimator (\extpsynth{})}\\

The \extpsynth{} estimator (Eq. \ref{eq:extpsynth}) has been proposed by \cite{mandallaz2013a} as a transformed version of the \psmall{} estimator that has the form of the \psynth{} estimator but remains asymptotically design unbiased. It has the advantage that the mean of the empirical model residuals of the OLS regression model for the entire area $F$ and the small area $G$ are by construction both zero at the same time, i.e. $\bar{\hat{R}}_{c} = \bar{\hat{R}}_{c,G} = 0$. This is realized by \textit{extending} the auxiliary vector $\pmb{Z}_{c}(x)$ by the indicator variable $I_{c,G}$ which takes the value 1 if the entire cluster lies within the small area $G$ and 0 if the entire cluster is outside $G$, i.e. $I_{c,G}(x)=\frac{M_{G}(x)}{M(x)}$. The extended auxiliary vector thus becomes $\pmb{\mathbb{Z}}_{c}^{\top}(x)= (\pmb{Z}_{c}^{\top}(x),I_{c,G}(x))$ and the new regression coefficient using $\pmb{\mathbb{Z}}_{c}(x)$ instead of $\pmb{Z}_{c}(x)$ in Eq. \ref{normequ_simple_cluster} is denoted as $\hat{\pmb{\theta}}_{s_2}$. All remaining components are calculated by plugging in $\pmb{\mathbb{Z}}_{c}(x)$ in Eq. \ref{eq:compsG}. A decomposition of $\hat{\pmb{\theta}}_{s_2}$ reveals that the residual correction term is now included in the regression coefficient $\hat{\pmb{\theta}}_{s_2}$.

@@

% ----------------------------- %
\subsection{Measures of estimation accuracy}

@@

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\section{Case study}
\label{sec:CaseStudy}

@@

\subsection{Study area and small area units}
\label{sec:studyarea}

The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium. With 42.3\% (appr. 8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}. The forests of RLP are further characterized by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterized by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a. Hunsr{\"u}ck and Palatinate forest) up to mixed forests comprising variable proportions of oak, larch, spruce, Scots pine and beech. Around 82\% of the forest area in RLP are mixed forest stands and 69\% of the forest area exhibit a multi-layered vertical structure. The forest area of RLP are divided into 3 ownership classes, i.e. state forest (27\%), communal forest (46\%) and privately owned forest (27\%). The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}. For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArea}). On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 426 Forstreviere (\textit{FR}). The next level are the actual forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5- to 10 year period in order to set up management strategies for the upcoming 10 years. The FAs and FRs constituted the small area (SA) units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}. The average area of the SA units were 43'777 ha on the FA-level, and 4624 ha on the FR level.

@@

% ----------------------------------------------------------------------- %
\subsection{Terrestrial sample}

Rhineland-Palatinate (RLP) is covered by a 2x2 km inventory grid of the German NFI. In the last inventory (BWI3) conducted in the year 2013, timber volume information was derived for 2810 cluster (8092 plots) in the field survey. The local timber volume density on the plot and cluster level for this sample was consequently calculated according to Section \ref{sec:srs_estimator}. In the frame of this survey, the plot center coordinates have been re-measured with differential global satellite navigation system (DGPS) technique. Knowledge about the exact plot positions were considered crucial to provide optimal comparability between the terrestrially observations and the information derived from the auxiliary information. A comparison of the DGPS coordinates with the so-far used target coordinates revealed that 90\% of all horizontal deviations lay in the range of 25 meters. A detailed analysis of horizontal DGPS errors in RLP by \citet{lambrecht2017} indicated that 80\% of the plots should not exceed horizontal DGPS errors of 8 meters. For 162 plots, the DGPS coordinates were replaced by their target coordinates due to missingness or implausible values.

% NOTE:
% - add table with overview of terrestrial dta attributes (like Johannes)
%

% ----------------------------------------------------------------------- %
\subsection{Extension to double sampling design}

In order to apply the small area estimators (Section (\ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 km grid to a 500x500 m sample grid that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}). The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ cluster by the terrestrially measured DGPS coordinates. For our study, we restricted the \textit{sampling frame} to the communal and state forest. The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service. The terrestrial sample size was thus reduced to 2055 cluster (5791 plots). Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.

\begin{figure}[H]
	\centering
	\resizebox{0.63\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
	\caption{\textit{Left}: Study Area with delineated FA forest management units. \textit{Right}: Example for each of the three management units (from top to bottom): FA, FR and forest stand unit with overlayed the extended double sampling cluster design. \textit{Green}: Forest stand polygon layer defining the forest area of this study.}
	\label{fig:StudyArea}
\end{figure}

@@

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Auxiliary information}
\label{sec:auxinfo}

% ----------------------------------------- %
\subsubsection{LiDAR canopy height model}
\label{sec:chm}

A prerequisite for the application of the suggested two-phase small area estimators was the identification of suitable auxiliary information that is available over the entire study area. Between the year 2003 and 2013, the topographic survey institution of RLP conducted an airborne laser scanning (LiDAR) acquisition over the entire federal state at leaf-off condition in order to derive a countrywide digital terrain and surface model. For this study, the recorded LiDAR data was used to create a canopy height model (CHM) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters (Figure \ref{fig:Auxvars}, \textit{top}). The CHM was calculated as the difference between the digital terrain model (DTM) and the digital surface model (DSM) that were derived by a Delauney interpolation of the two separated LiDAR point clouds (ground pulses and first pulses from non-ground objects). Based on numerous studies (e.g. \cite{maack2016}), the CHM was considered to provide the most valuable information to be used in the OLS regression model for predicting the timber volume on sample plot level. However, during the extended acquisition period, airborne laser scanning technology evolved significantly, which lead to severe quality variations in the CHM. In particular, the LiDAR acquisition recorded in 2002 and 2003 exhibited a rather poor quality with about only 1 point per 5x5 m$^2$, while more recently acquired datasets contained more than 125 points per 5x5 m$^2$ raster cell. Furthermore, due to sensor failures, CHM information was not available at 16 sample locations (none of them considered terrestrial sample plots of the $s_2$ phase though). These plots were deleted from the sampling frame and its non-available information thus treated as missing at random. This assumption was considered to be reasonable as the respective sample locations did not exclude specific forest structures.

@@

% ---------------------------------------------- %
\subsubsection{Tree species map}
\label{sec:tspecclass}

The second source of auxiliary information was a countrywide satellite-based classification map of the five main tree species (European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir, Scots pine) described in \citet{stoffels2015} (Figure \ref{fig:Auxvars}, \textit{bottom}). The classified tree species map has a grid size of 5 meters and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) by application of the spatially adaptive classification algorithm described in \citet{stoffels2012}.  As timber volume estimations on the tree level are often based on species-specific biomass and volume equations, the use of tree species information - especially for timber volume estimation - has often been stated as a key factor for improving the estimation precision \cite{white2016}. In this respect, incorporating the tree species map information was particularly attractive as it predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree. However, due to unavailable satellite data for the classification, the tree species map excluded one large patch with an area of 415 km$^2$ in the south-west part of RLP covering an entire FA-unit (10 FR units respectively). In 9 additional FR units, the tree species information was also missing for a subset of the sample locations due to two additional patches with an area of 76 km$^2$ and 100 km$^2$ in the northern part of RLP. For these parts, small area estimation was thus restricted to using only the available CHM information in the regression model. With respect to model fitting, the tree species information was missing for 407 (7\%) of the 5791 sample locations. A summary of the sample sizes and missing auxiliary information is again provided in Table \ref{tab:ssize}.

% Graphik:
\begin{figure}[H]
	\centering
	\resizebox{0.8\hsize}{!}{\includegraphics*{fig/AuxvarsLOWRES.png}}
	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information. Right: Magnified illustration of the rectangular supports used to derive the explanatory variables from the auxiliary information.}
	\label{fig:Auxvars}
\end{figure}

\begin{table}[H]
	\begin{center}
		\caption{Sample size for each phase in entire study area. $n_{\{1,2\},plots}$: number of plots. $n_{\{1,2\}}$: number of cluster}
		\vspace{0.2cm}
		\label{tab:ssize}
		{\small %
		\begin{tabular}{l|r|r|r|r}
			\hline
			\multicolumn{1}{c|}{\textit{Sampling frame}} & \multicolumn{1}{c|}{\textbf{$n_{1,plot}$}}  & \multicolumn{1}{c|}{\textbf{$n_1$}}  & \multicolumn{1}{c|}{\textbf{$n_{2,plot}$}}  & \multicolumn{1}{c}{\textbf{$n_2$}} \\ % <-- added & and content for each column
			\hline \hline
			communal and state forest & 96'854 & 33'365 & 5791 & 2055\\ % <--
			\hspace{5mm} \footnotesize missing CHM & \footnotesize 16 & \footnotesize 9 & \footnotesize 0 & \footnotesize 0\\ % <--
			\hspace{5mm} \footnotesize missing TSPEC & \footnotesize 6910  & \footnotesize 3465 & \footnotesize 407 & \footnotesize 380\\ % <--
			\hspace{5mm} \footnotesize missing CHM \textit{and} TSPEC & \footnotesize 2 & \footnotesize 1 & \footnotesize 0 & \footnotesize 0\\ % <--
			\hspace{5mm} \footnotesize missing CHM \textit{or} TSPEC & \footnotesize 6924 & \footnotesize 3473 & \footnotesize 407 & \footnotesize 380\\ % <--
			\hline \hline
		\end{tabular}
	} %
	\end{center}
\end{table}

%\begin{table}[H]
%	\begin{center}
%		\caption{Sample size for each phase in entire study area.}
%		\label{tab:ssize}
%		\begin{tabular}{l|r|r|r|r}
%			\hline
%			\textit{Sampling frame} & \textbf{$n_{1,plot}$} & \textbf{$n_1$} & \textbf{$n_{2,plot}$} & \textbf{$n_2$}\\ % <-- added & and content for each column
%			\hline \hline
%			communal and state forest & 96'854 & 33'365 & 5791 & 2055\\ % <--
%			\hspace{5mm} \small missing CHM & \small 16 & \small 9 & \small 0 & \small 0\\ % <--
%			\hspace{5mm} \small missing TSPEC & \small 6910  & \small 3465 & \small 407 & \small 380\\ % <--
%			\hspace{5mm} \small missing CHM \textit{and} TSPEC & \small 2 & \small 1 & \small 0 & \small 0\\ % <--
%			\hspace{5mm} \small missing CHM \textit{or} TSPEC & \small 6924 & \small 3473 & \small 407 & \small 380\\ % <--
%			\hline
%			Total for estimation & 89'930 & 29'892 & 5384 & 1675\\ % <--			
%		\end{tabular}
%	\end{center}
%\end{table}

% ---------------------------------------------- %
\subsection{Calculation of the auxiliary variables}
\label{sec:expvarcalc}

\subsubsection{LiDAR canopy height model}

From the CHM, the mean canopy height (\textit{meanheight}) and the standard deviation (\textit{stddev}) was calculated by evaluating the raster values around each sample location within a predefined rectangular square (support) with a side length of 12 meters that was centered around the sample plot centers. Each support was previously intersected with the forest polygon layer in order to evaluate auxiliary information only within the forest definition. The percentage of the non-intersected support within the forest layer was used as the weight $w(x_l)$ introduced in  Eq. \ref{eq:Zc(x)}. Furthermore, the year of the LiDAR acquisition (\textit{lidaryear}) was derived as an additional categorical variable to account for the time-lag between the CHM information and the terrestrial survey as well as to explain heterogeneity in the data introduced by the varying LiDAR quality. Adjustments were made to the original acquisition years by introducing an additional factor level \textit{2008\_1} for a subset of the 2008 acquisition where the quality turned out to be considerably poor due to a sensor error. In addition, the years 2006 and 2007 as well as 2012 and 2013 were pooled in order to increase the number of observations per factor level, resulting in nine categories in total (\textit{2002}, \textit{2003}, \textit{2007}, \textit{2008\_1}, \textit{2008}, \textit{2009}, \textit{2010}, \textit{2011} and \textit{2012}).

\subsubsection{Tree species map}

The tree species map information was used to predict the main tree species of a sample plot (\textit{treespecies}). This implied two consecutive processing steps. In the \textit{first} step, one of the five tree species was assigned to a sample location if 100\% of the raster values within the same support as used for the CHM were classified as that species. Otherwise, the sample location was assigned the value 'mixed'. It should be mentioned that the support size and the percentage threshold are parameters that can be optimised in order to achieve the best variance decomposition and thus improvement in model accuracy when using the categorical \textit{treespecies} variable in a regression model. \citet{hill2017a} conducted a detailed analysis of how to optimally derive the auxiliary variables for the present data set and identified the above described settings as the most suitable. It was additionally shown that using the random forest algorithm by \citet{breiman2001} for a calibration of the predicted main plot species on the actual main taper-function species derived from the terrestrial inventory data could boost the classification accuracy in the classes \textit{Scots pine} and \textit{Douglas Fir}, which performed considerably worse than the remaining species (Table \ref{tab:classacc}). The calibration was able to considerably mitigate the effects of misclassification on the regression coefficients and thus allowed for an increase in model accuracy. In a \textit{second} step, we thus provided the random forest algorithm in the statistical software R \citep{R} with the actual main taper-function species derived from the terrestrial inventory data as response variable as well as a full set of $p$ predictor variables that comprised the initial prediction of the main plot tree species (\textit{treespecies}), the mean canopy height (\textit{meanheight}) and standard deviation ($stddev$) derived from the CHM, the proportion of coniferous trees estimated from the tree species classification map ($prop.conif$) and the bioclimatic growing region ($wgb$) at the sample location. The algorithm was grown with 2000 trees, considering $\sqrt{p} \approx$ 3 of the predictors for each split. The resulting random forest model was consequently applied at all sample locations $s_1$ to provide the \textit{treespecies} variable.

\begin{table}[H]
	\begin{center}
	\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
	\vspace{0.2cm}
	\label{tab:classacc}
 {\small %
	\begin{tabular}{c|c|c|c|c|c|c|c} %8cols
		\hlineB{1}
		\multirow{2}{*}{Main plot species} & \multicolumn{2}{c|}{Producer's accuracy[\%]} & \multicolumn{2}{c|}{User's accuracy[\%]} & \multirow{2}{*}{nref} & \multicolumn{2}{c}{nclass} \\ 
		\cline{2-3} \cline{4-5} \cline{7-8} & uncalib & calib & uncalib & calib & & uncalib & calib \\
		\hline \hline	
		 Beech       & 29.56 & 22.31 & 46.11 & 47.02 & 883 & 566 & 419 \\
		 Douglas Fir & 33.04 & 24.78 & 47.50 & 48.72 & 230 & 160 & 117 \\
		 Oak         & 47.75 & 11.07 & 24.34 & 48.48 & 289 & 567 & 66 \\
		 Spruce      & 43.63 & 53.15 & 60.81 & 61.13 & 651 & 467 & 566 \\
		 Scots Pine  & 55.87 & 22.91 & 29.59 & 46.07 & 179 & 338 & 89 \\
		 Mixed       & 66.40 & 84.49 & 63.69 & 64.53 & 3152 & 3286 & 4127 \\
		\hline
		 & \multicolumn{4}{l|}{Overall accuracy: 54.83\% (61.96\%)} & 5384 & \multicolumn{2}{c}{5384} \\
		 \hline \hline
	\end{tabular}
}%
	\end{center}
\end{table}

% ---------------------------------------------- %
\subsection{Regression Model}
\label{sec:regmod}

% NOTES:
% - model formulation was based on the following considerations: a) The mean canopy height has the heighest explanatory power. Since the strength of correlation between meanheight and the timber volume on plot level showed high variation according to the time-lag of up to 10 years between the LiDAR acquisition and the BWI3 terrestrial inventory. and the varying LiDAR quality, the 
%
%
%
%
%

% MENTION:
% - objective: find regression model (formula) to be applied in the sae estimators
% - Specialty here: in the sae estimators, the predictions are generated on the cluster level (thus the regression coefficients are found on the cluster level)
%   (--> and even more important: the residuals considered in the variance est. are also on the cluster level)
%  ==> so for model selection, we looked at the global model performance on the plot as well as the cluster level
%  ==> we also performed individual paramater t-test for each variable on the plot and cluster level. In order to  
%
% - important to recall that the design-based estimators, in which the regression model is used, do not impose any assumptions on the regression model as is the case in the model-dependent estimation framework.
%
% - no terrestrial data removed from the dataset for modelling, as all terrestrial data are used in the internal model (no choice, its specified by the estimators) 
%
% - mention sample sizes here: Due to missingness in the rs-data, the auxiliary variables were calculated for 89'930 sample plots (5384 terrestrial ...)
%
% - Model Validation (compare several models in table --> Alex)
%
% - Design-based Model Inference (new, use design-based var-covar-matrix)
%
% - idea: make a design-based inference of the regression coefficients on cluster level on the robust reg.coef-matrix
%   "whereas the regression analysis in hill et al. 2017a" was carried out on the sample plot level, we here extend
%    the analysis to the cluster level, as this is actually the level the estimators use the regression model predictions"
%

% ---------------------------------------------- %
\subsubsection{Design-Based Model Inference}
\label{sec:edbinf}

>>>>

\section{Methods}
\label{sec:Meth}

@@

\subsection{Terrestrial Sampling Design of the German NFI}
\label{sec:germanNFI}

@@

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Estimators}
\label{sec:estimators}

% ++++++++++++ %
\subsubsection{Double Sampling in the Infinite Population Approach}
\label{sec:inf_pop}

@@

% ++++++++++++ %
\subsubsection{SRS Estimator for Cluster Sampling}
\label{sec:srs_estimator}

The simple random sampling (SRS) estimator for cluster sampling was applied under the existing one-phase sampling design of the German NFI in order to obtain a point and variance estimate for the mean timber volume in each small area unit (Section \ref{sec:studyarea}). In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator in the form given in \citet{mandallaz2008, mandallaz2016}. In order to calculate the local density $Y_{c}(x)$ at the cluster level, a cluster is defined as consisting of $M$ sample locations (in the BWI3, we have $M=4$ ) where $M-1$ sample locations $x_2, ..., x_M$ are created close to the cluster origin $x_1$ by adding a fixed set of spatial vectors $e_2, ..., e_M$ to $x_1$. The actual number of plots per cluster, $M(x)$, is a random variable due to the uniform distribution of $x_l$ ($l=1, ..., M$) in the forest $F$ and forest/non-forest decision for each sample location $x_l$:

@@

% +++++++++++++++++++++++++++++ %
\subsubsection{Design-Based Small Area Regression Estimators for Cluster Sampling}
\label{sec:SAestimators}

@@

% ----------------------------- %
% PSMALL estimator:
\textbf{Pseudo Small Area Estimator (\psmall{})}\\

@@

The estimated design-based variance of $ \hat{Y}_{c,G,PSMALL}$ is given by Eq. \ref{eq:psmall_var}. Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean using the sample $s_{1,G}$. The third term is the variance of the model residuals and thus accounts for the inaccuracies of the model predictions. Note that the first term can also be rewritten using g-weights \cite[pg.14]{mandallaz2016} which ensure calibration properties of the auxiliary variables on the terrestrial sample.\\

@@

% ----------------------------- %
% PSYNTH estimator:
\newpage
\textbf{Pseudo Synthetic Estimator (\psynth{})}\\

@@

% ----------------------------- %
% EXTPSYNTH estimator:
\textbf{Extended Pseudo Synthetic Estimator (\extpsynth{})}\\

The \extpsynth{} estimator (Eq. \ref{eq:extpsynth}) has been proposed by \cite{mandallaz2013a} as a transformed version of the \psmall{} estimator that has the form of the \psynth{} estimator but remains asymptotically design unbiased. It has the advantage that the mean of the empirical model residuals of the regression model for the entire area $F$ and the small area $G$ are by construction both zero at the same time, i.e. $\bar{\hat{R}}_{c} = \bar{\hat{R}}_{c,G} = 0$. This is realized by \textit{extending} the auxiliary vector $\pmb{Z}_{c}(x)$ by the indicator variable $I_{c,G}$ which takes the value 1 if the entire cluster lies within the small area $G$ and 0 if the entire cluster is outside $G$, i.e. $I_{c,G}(x)=\frac{M_{G}(x)}{M(x)}$. The extended auxiliary vector thus becomes $\pmb{\mathbb{Z}}_{c}^{\top}(x)= (\pmb{Z}_{c}^{\top}(x),I_{c,G}(x))$ and the new regression coefficient using $\pmb{\mathbb{Z}}_{c}(x)$ instead of $\pmb{Z}_{c}(x)$ in Eq. \ref{normequ_simple_cluster} is denoted as $\hat{\pmb{\theta}}_{s_2}$. All remaining components are calculated by plugging in $\pmb{\mathbb{Z}}_{c}(x)$ in Eq. \ref{eq:compsG}. A decomposition of $\hat{\pmb{\theta}}_{s_2}$ reveals that the residual correction term is now included in the regression coefficient $\hat{\pmb{\theta}}_{s_2}$.

@@

\subsubsection{Measures of Estimation Accuracy}

@@

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\section{Materials}
\label{sec:Mat}

@@

\subsection{Study Area and Small Area Units}
\label{sec:studyarea}

The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium (figure \ref{fig:Study Area}). With 42.3\% (appr. 8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}. The forests of RLP are further characterized by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterized by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a. Hunsr{\"u}ck and Palatinate forest) up to mixed forests comprising variable proportions of oak, larch, spruce, Scots pine and beech. Around 82\% of the forest area in RLP are mixed forest stands and 69\% of the forest area exhibit a multi-layered vertical structure. The forest area of RLP are divided into 3 ownership classes, i.e. state forest (27\%), communal forest (46\%) and privately owned forest (27\%). The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}. For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (figure xx). On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 426 Forstreviere (\textit{FR}). The next level are the actual forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5- to 10 year period in order to set up management strategies for the upcoming 10 years. The FAs and FRs constituted the small area (SA) units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}. The average area of the SA units were 43'777 ha on the FA-level, and 4624 ha on the FR level.\\

@@

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Extension to Double Sampling Design}

Rhineland-Palatinate (RLP) is covered by a 2x2 km inventory grid of the German NFI, where timber volume information was derived for 2810 cluster (8092 plots) in the field survey of the latest inventory. The local timber volume density on the plot and cluster level for this sample was consequently calculated according to Section \ref{sec:srs_estimator}. In the frame of the last inventory (BWI3), the plot center coordinates have been re-measured with differential global satellite navigation system (DGPS) technique. Knowledge about the exact plot positions were considered crucial to provide optimal comparability between the terrestrially observations and the information derived from the auxiliary information. A comparison of the DGPS coordinates with the so-far used target coordinates revealed that 90\% of all horizontal deviations lay in the range of 25 meters. A detailed analysis of horizontal DGPS errors in RLP by \citet{lambrecht2017} indicated that 80\% of the plots should not exceed horizontal DGPS errors of 8 meters. For 162 plots, the DGPS coordinates were replaced by their target coordinates due to missingness or implausible values.\par

In order to apply the small area estimators (Section (\ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 km grid to a 500x500 m sample grid that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure xx). The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ cluster by the terrestrially measured DGPS coordinates. For our study, we restricted the \textit{sampling frame} to the communal and state forest. The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service. The terrestrial sample size was thus reduced to 2055 cluster (5791 plots). Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.\par

\begin{figure}[H]
	\centering
	\resizebox{0.75\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
	\caption{Forest management units in Rhineland-Palatinate, overlayed with the extended double sampling cluster design.}
	\label{fig:StudyArea}
\end{figure}

@@

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Auxiliary Information}
\label{sec:auxinfo}

% ! Mention Missingness in the data and resulting reduction of the sample size (s1, s2)

% ----------------------------------------- %
\subsubsection{LiDAR Canopy Height Model}
\label{sec:chm}

In order to derive a countrywide digital terrain and surface model, the topographic survey institution of RLP conducted an airborne laser scanning (LiDAR) acquisition over the entire federal state at leaf-off condition between the year 2003 and 2013. For this study, these data was used to create a canopy height model (\textit{CHM}) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters. The CHM was calculated as the difference between the digital terrain model (DTM) and the digital surface model (DSM) that were derived by a Delauney interpolation of the two separated LiDAR point clouds (ground pulses and first pulses from non-ground objects). During the extended acquisition period, airborne laser scanning technology and data quality evolved significantly, which lead to severe variations in the data quality. In particular, the LiDAR acquisition recorded in 2002 and 2003 exhibited a rather poor quality with about only 1 point per 5x5 m$^2$, while more recently acquired datasets of contain more than 125 points per 5x5 m$^2$ raster cell. Due to sensor failures, CHM information was not available at 16 $s_1$ (0 $s_2$) sample points.

@@

% ---------------------------------------------- %
\subsubsection{Tree Species Classification Map}
\label{sec:tspecclass}

A countrywide satellite-based classification map of the five main tree species (European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir, Scots pine) described in \citet{stoffels2015} was used to derive tree species information on sample plot level. The classified tree species map has a grid size of 5 meters and predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree. Due to unavailable satellite data for the classification, the tree species map excluded one patch with an area of 415 km$^2$ in the south-west part of RLP, and two further patches with an area of 76 km$^2$ and 100 km$^2$ in the northern part \citep{stoffels2015}. The tree species information was consequently missing for 407 (7\%) of the 5791 sample locations.

%
%
%
%
%
%

% ---------------------------------------------- %
\subsubsection{Calculation of Explanatory Variables}
\label{sec:tspecclass}

% Graphik:

%\begin{figure}[H]
%	\centering
%	\resizebox{0.8\hsize}{!}{\includegraphics*{fig/Auxvars.png}}
%	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information. Right: Magnified illustration of the rectangular supports used to derive the explanatory variables from the auxiliary information.}
%	\label{fig:Auxvars}
%\end{figure}

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Regression Model}
\label{sec:regmod}
